### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS. The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory. We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Safe Password Checker& 65536& 16.0\\
Unsafe Password Checker & 65536 & 16.0\\
One-byte Lookup Table & 65536 & 16.0\\
Four-byte Lookup Table & 65536 & 16.0\\
AES mbedTLS 2.15 & 65536 & 16.0   \\
AES OpenSSL 1.1.0  & 65536 & 16.0    \\
AES OpenSSL 1.1.1& 65536 & 16.0 \\
AES wolfSSL 4.5.0& 65536 & 16.0\\
AES Libgcrypt 1.8.7& 65536 & 16.0\\
RC4 mbedTLS 2.15& 65536 & 16.0\\
RC4 OpenSSL 1.1.0& 65536 & 16.0\\
RC4 OpenSSL 1.1.1& 65536 & 16.0\\
RC4 wolfSSL 4.5.0& 65536 & 16.0\\
RSA mbedTLS 2.15& 4096 & 12.0\\
RSA OpenSSL 1.1.0& 4096 & 12.0\\
RSA OpenSSL 1.1.1& 4096 & 12.0\\
RSA wolfSSL 4.5.0& 4096 & 12.0\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
Tiny DNN & 12000 & 13.6 &\\
GDK 3.24.23 & 65535 & 16.0 &\\
\bottomrule
\end{tabular}

@@

\subsection{Benchmarks}
\subsubsection{Password Checker}

\subsubsection{Lookup Table}

\subsection{Cryptography Library}

>>>>

\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS. The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory. We use the default release settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits &  1 Byte & 64 Bytes & 4 KBs & 1 Byte & 64 Bytes & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0& & & & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0&0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0\\
Four-byte Lookup Table & 65536 & 16.0\\
AES mbedTLS 2.15 & 65536 & 16.0   \\
AES OpenSSL 1.1.0  & 65536 & 16.0    \\
AES OpenSSL 1.1.1& 65536 & 16.0 \\
AES wolfSSL 4.5.0& 65536 & 16.0\\
AES Libgcrypt 1.8.7& 65536 & 16.0\\
RC4 mbedTLS 2.15& 65536 & 16.0\\
RC4 OpenSSL 1.1.0& 65536 & 16.0\\
RC4 OpenSSL 1.1.1& 65536 & 16.0\\
RC4 wolfSSL 4.5.0& 65536 & 16.0\\
RSA mbedTLS 2.15& 4096 & 12.0\\
RSA OpenSSL 1.1.0& 4096 & 12.0\\
RSA OpenSSL 1.1.1& 4096 & 12.0\\
RSA wolfSSL 4.5.0& 4096 & 12.0\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
Tiny DNN & 12000 & 13.6 &\\
GDK 3.24.23 & 65535 & 16.0 &\\
\bottomrule
\end{tabular}

@@

\subsection{Benchmarks}
\subsubsection{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The right version is vulnerable to side-channel attacks. The left version is the fixed version.}\label{fig:chapter5:pwcheck}
\end{figure}

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint8_t T[16] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
...
output = (T[(key[i]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint32_t T[16] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[i+0]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
\end{figure}
\subsection{Cryptography Library}
